Gaudeamus Figures

### 2016-11-10 inst/examples/Gaudeamus.Rmd
ok

```{r Gaudeamus_Vaasa, echo=FALSE, fig.width=20, fig.height=10}
df <- dfo
df <- df %>% filter(!is.na(publication_year))
tmp1 <- df %>% filter(publication_place == "Vaasa") %>%
     	       group_by(publication_year) %>%
	       tally() %>%
	       arrange(publication_year)
tmp1$decade <- as.numeric(paste0(substr(tmp1$publication_year,1,3),"0"))
tmp2 <- tmp1 %>% group_by(decade) %>% summarise(m = sum(n)/10)
final <- inner_join(tmp1,tmp2)

par(las=1)
par(mgp=c(10,3,0))
par(mar=c(7,17,6,4))
plot(final$publication_year,final$n,cex=1.5,pch="|",cex.main=4.0,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=4.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
lines(final$publication_year,final$m,type="l",lty=3,col="black",lwd=4)
axis(side = 1, at = c(1764,1809,1863,1917),cex.axis=3)
axis(side = 2, at = c(0,40,80,120,160,194),cex.axis=3)
remove(tmp1,tmp2,final)
```

>>>>

```{r Gaudeamus_Vaasa, echo=FALSE, fig.width=20, fig.height=10}
df <- dfo
df <- df %>% filter(!is.na(publication_year))
tmp1 <- df %>% filter(publication_place == "Vaasa") %>%
     	       group_by(publication_decade, publication_year) %>%
	       tally() %>%
	       arrange(publication_year)

#tmp1$decade <- as.numeric(paste0(substr(tmp1$publication_year,1,3),"0"))
tmp2 <- tmp1 %>% group_by(publication_decade) %>% summarise(m = sum(n)/10)

years <- c(1764,1809,1863,1917)
p <- ggplot(tmp1, aes(x = publication_year, y = n)) +
       geom_point() +
       geom_bar(aes(x = publication_decade + 5, y = m), stat = "identity", fill = "gray", alpha = 0.9, color = "black", data = tmp2) +
       ggtitle("Julkaisutoiminta Vaasassa 1764-1917") +
       ylab("Dokumenttia / vuosi") +
       scale_x_continuous(labels = years, breaks = years) +
       xlab("Julkaisuvuosi")

print(p)
```
